Notes on Design and Implementation of Anglican

### 2015-07-18 paper/paper.tex
in progress

Operational semantic of Anglican queries is different from that
of Clojure code, therefore queries must be called through
inference algorithms, rather than `directly'.

>>>>

Operational semantic of Anglican queries is different from that
of Clojure code, therefore queries must be called through
inference algorithms, rather than `directly'.  The
\texttt{anglican.inference} namespace supplies the
\texttt{infer} multimethod, which accepts an Anglican query and
returns a lazy sequence of weighted samples from the
distribution defined by the query. Inference algorithms must
provide an implementation for \texttt{infer}, as well as
override some of the methods of the \textit{checkpoint}
multimethod, called to handle \texttt{sample} and
\texttt{observe} in an algorithmic-specific manner, as well
as on termination of a probabilistic program.
